\documentclass[10pt,letterpaper]{article}
\usepackage{geometry}
\geometry{letterpaper, portrait, margin=1in}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{array}
\usepackage{hyperref}
\usepackage{adjustbox,lipsum}
\usepackage{gensymb}
\usepackage{enumerate}
\setlength{\parindent}{0pt}
\renewcommand\refname{References}

\begin{document}
\title{\scshape\LARGE University of Waterloo \vfill \huge\bfseries PHYS 437A Assignment 2 \vfill}
\author{Robert Burnet \\ rcburnet@uwaterloo.ca \\ 20465122 }
\maketitle

\newpage

This week, I compared my list of 284 primaries to Ryan's list of 274 primaries to check if the extra 10 in my list were the ones missing in Ryan's list and why Ryan excluded them.\\

I made a script called ``284\_primaries\_compared\_to\_274.py" to compare the two lists and print the primaries in my list that were missing from Ryan's list. When I did that, instead of getting back 10 extra primaries, I got back 23. 23 primaries in my list that weren't in Ryan's list. These were primaries that Ryan cut that I did not cut. Namely:\\

\begin{enumerate}
\item NGC2549
\item PGC042549
\item NGC0573
\item NGC0864
\item NGC1012
\item NGC1924
\item NGC2690
\item NGC3359
\item NGC4348
\item NGC4602
\item NGC4604
\item NGC4691
\item NGC6015
\item NGC6070
\item NGC6118
\item NGC6339
\item NGC6384
\item NGC6675
\item NGC7814
\item PGC005363
\item UGC03258
\item UGC10288
\item UGC12857
\end{enumerate}

I then went back to last week's script to see what was going on. I found out that there was a discrepancy between my cut of primaries not within the SDSS survey and Ryan's cut. I had cut 64 primaries in that cut, as the SDSS DR8 CrossID tool did not give back those primaries when I queried them in the database (ie. these galaxies were not within 0.5 arcminutes of a detection in SDSS). However, 13 of those primaries were in Ryan's list of 274 primaries. These were primaries I cut that Ryan did not cut. Using the SDSS DR8 Navigate Tool \cite{navigate}, these 13 were in fact in SDSS. The CrossID tool was not sufficient at providing all the primaries that were in SDSS that I queried. The 13 primaries that I should not have cut were namely:\\

\begin{enumerate}
\item NGC0628
\item NGC1073
\item NGC2775
\item NGC2903
\item NGC3169
\item NGC3184
\item NGC3344
\item NGC4559
\item NGC4725
\item NGC4736
\item NGC5005
\item NGC5371
\item NGC7714
\end{enumerate}

So in all, I had 23 extra primaries in my final list, not the expected 10, from Ryan's list and Ryan had 13 primaries which I cut from my list. That means I cut 13 that I shouldn't have cut, leaving me with 297 primaries, not 284 primaries after applying the second cut, and 23 primaries extra which are in badly masked regions or regions of incomplete coverage. This would leave me with 284 + 13 - 23 = 274 primaries - the same as Ryan.\\

I checked to make sure my first and third cuts were applied properly. This involved writing in last week's script, ``871\_to\_274\_cuts.py", code which looked into each list of cut primaries for each cut and making sure each primary that I cut was not in Ryan's list (ie. the first and third cuts I applied were the same primaries that Ryan cut). Both the first and third cuts cut primaries that Ryan also cut. Therefore, the 23 extra primaries Ryan must have cut in his second cut, and they must have been primaries in badly masked regions, or regions of incomplete coverage.\\

To check why Ryan cut these extra 23 primaries (why they were in badly masked regions or regions of incomplete coverage), I queried the 23 primaries in the SDSS DR8 Navigate Tool. I provide reasoning for why they are cut, as well as pictures to support my reasoning.\\

\begin{enumerate}
\item NGC0628 - can't seem to find out why this was cut from Ryan's list.
\item NGC1073
\item NGC2775
\item NGC2903
\item NGC3169
\item NGC3184
\item NGC3344
\item NGC4559
\item NGC4725
\item NGC4736
\item NGC5005
\item NGC5371
\item NGC7714
\end{enumerate}




\newpage
\center
\begin{thebibliography}{1}
\bibitem{Atlas3D} Cappellari, M., Emsellem, E., Krajnovi\'c, D., et al. 2011, MNRAS, 413, 813\\

\bibitem{classic SDSS} Classic Sloan Digital Sky Survey. (n.d.). Retrieved September 18, 2016, from \url{http://classic.sdss.org/}\\

\bibitem{Vaucouleurs} de Vaucouleurs, G., de Vaucouleurs, A., Corwin, H. G., Jr., et al. 1991, Third
Reference Catalogue of Bright Galaxies (New York: Springer)\\

\bibitem{Fukugita} Fukugita, M., Shimasaku, K., \& Ichikawa, T. 1995, PASP, 107, 945\\

\bibitem{Great Circle Drift Scanning} Great Circle Drift Scanning. (n.d.). Retrieved September 25, 2016, from \url{http://classic.sdss.org/dr7/products/general/edr_html/node26.html}\\

\bibitem{NED 871} NED results for object(s) in publication ``2011MNRAS.413..813C" (n.d.). Retrieved September 21, 2016, from \url{https://ned.ipac.caltech.edu/cgi-bin/nph-objsearch?search_type=Search&refcode=2011MNRAS.413..813C}

\bibitem{SDSS-III} SDSS-III. (n.d.). Retrieved September 20, 2016, from \url{https://www.sdss3.org/}\\

\bibitem{CrossID} SDSS CrossID for DR8. (n.d.). Retrieved September 26, 2016, from \url{http://cas.sdss.org/dr8/en/tools/crossid/crossid.asp}\\

\bibitem{navigate} SDSS DR8 Navigate Tool. (n.d.). Retrieved October 01, 2016, from \url{http://skyserver.sdss.org/dr8/en/tools/chart/navi.asp}\\

\bibitem{scope} SDSS Scope. (n.d.). Retrieved September 20, 2016, from \url{http://www.sdss.org/dr13/scope/}\\

\bibitem{Survey Coordinates} SDSS Survey coordinates. (n.d.). Retrieved September 25, 2016, from \url{https://www.sdss3.org/dr10/algorithms/surveycoords.php}\\

\bibitem{SQL tutorial} Searching for Data: A Tutorial. (n.d.). Retrieved September 18, 2016, from \url{http://skyserver.sdss.org/dr12/en/help/howto/search/searchhowtohome.aspx}\\

\bibitem{2MASS} Skrutskie, M. F., Cutri, R. M., Stiening, R., et al. 2006, AJ, 131, 1163\\

\bibitem{DR7 sky coverage} Sky coverage. (n.d.). Retrieved September 25, 2016, from \url{http://classic.sdss.org/dr7/coverage/}\\

\bibitem{SDSS webpage} Sloan Digital Sky Surveys. (n.d.). Retrieved September 18, 2016, from \url{http://www.sdss.org/surveys/}\\

\bibitem{instruments} Telescopes and Instruments. (n.d.). Retrieved September 20, 2016, from \url{http://www.sdss.org/instruments/}\\

\bibitem{DR8} The Eighth SDSS Data Release (DR8). (n.d.). Retrieved September 20, 2016, from \url{https://www.sdss3.org/dr8/}\\

\bibitem{DR9} The Ninth SDSS Data Release (DR9). (n.d.). Retrieved September 20, 2016, from \url{https://www.sdss3.org/dr9/}\\

\bibitem{SDSS} York, D. G., Adelman, J., Anderson, J. E., Jr., et al. 2000, AJ, 120, 1579\\

\bibitem{schema} Schema Browser. (n.d.). Retrieved September 18, 2016, from \url{http://skyserver.sdss.org/dr12/en/help/browser/browser.aspx}\\

\end{thebibliography}

\end{document}