\documentclass[10pt,letterpaper]{article}
\usepackage{geometry}
\geometry{letterpaper, portrait, margin=1in}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{array}
\usepackage{hyperref}
\usepackage{adjustbox,lipsum}
\usepackage{gensymb}
\usepackage{enumerate}
\usepackage{listings}
\setlength{\parindent}{0pt}
\renewcommand\refname{References}

\begin{document}
\title{\scshape\LARGE University of Waterloo \vfill \huge\bfseries PHYS 437A Assignment 2 \vfill}
\author{Robert Burnet \\ rcburnet@uwaterloo.ca \\ 20465122 }
\maketitle

\newpage
I have found a way to query SDSS to determine whether or not an object is in the SDSS survey through CasJobs \cite{casjobs}. First, you must import a table of RA and DEC of the objects you wish to check are in the SDSS survey to your ``MyDB" database on CasJobs, an example table is shown below:\\

\begin{table}[h!]
\footnotesize
\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l|l|}
NAME & RA & DEC & SBF & NED\_D & Virgo & VHel & D & M\_K & A\_B & T\_type & log\_RE \\
\hline
IC0598 & 153.202423 & 43.145546 & 0 & 0 & 0 & 2256 & 35.3 & -22.60 & 0.06 & -0.1 & 1.02\\
IC0719 & 175.077042 & 9.009861 & 0 & 0 & 0 & 1833 & 29.4 & -22.70 & 0.22 & -2.0 & 1.10\\
IC3631 & 189.950195 & 12.973927 & 0 & 0 & 0 & 2822 & 42.0 & -22.01 & 0.17 & -1.3 & 1.13\\
NGC0448 & 18.818876 & -1.626105 & 1 & 1 & 0 & 1908 & 29.5 & -23.02 & 0.26 & -2.5 & 1.05\\
\end{tabular}
\end{table}

This table can be a comma or tab delimited text or csv file. On my ``MyDB" database, I called this table ``MyTable\_0". Then, you can perform the following SQL query on CasJobs under the DR8 context to retrieve the names of the objects in your table that are in SDSS:\\

\begin{lstlisting}[language=SQL]
SELECT 
  t.NAME
FROM mydb.MyTable_0 AS t 
WHERE 
  dbo.fInFootprintEq(t.ra, t.dec, 0.1) = 1
\end{lstlisting}

The query selects all the names of the objects in my table and uses the DR8 function fInFootprintEq to check if the area specified by the object's RA, DEC, and a chosen angular radius (0.1 arcminutes in the above example) is in SDSS. fInFootprintEq returns 1 as ``True" (ie. object is in SDSS) and 0 as ``False". \\

Using the above method, after applying the first cut in Ryan's paper which left me with 356 primaries, I am left with 315 primaries that are within the SDSS survey area. 8 of those are to be cut in the third cut (primaries near Coma, Leo, or Virgo clusters), leaving me with 33 primaries (315 - 8 - 274) that Ryan must have cut due to being in badly masked regions or regions of incomplete coverage.\\

I chose to write my own code to determine the masked regions and find areas of masked regions as Mangle \cite{mangle} was not sufficient for this task.\\

Why doesn't this work:\\

\begin{lstlisting}[language=SQL]
SELECT 
  p0.objid, p0.ra, p0.dec
FROM 
  mydb.primaries_in_sdss_315 as t, 
  PhotoObj as p0
JOIN dbo.fGetNearestObjEq(t.ra,t.dec,1) AS p1 ON p0.objid = p1.objid
\end{lstlisting}

I want the above to query SDSS to find the nearest object in SDSS to each of the 315 primaries that I found are in SDSS and retrieve the object ID so that I can use Ryan's SQL query (which joins by object ID) to find nearby objects. The above gives me error: \\

The multi-part identifier "t.ra" could not be bound. The multi-part identifier "t.dec" could not be bound.\\

But why doesn't that error pop up in my first SQL query which uses t.ra and t.dec on the similar function finFootprintEq?

\newpage
\center
\begin{thebibliography}{1}
\bibitem{image masks} Algorithms: Image masks. (n.d.). Retrieved October 02, 2016, from \url{https://www.sdss3.org/dr8/algorithms/masks.php}\\

\bibitem{Atlas3D} Cappellari, M., Emsellem, E., Krajnovi\'c, D., et al. 2011, MNRAS, 413, 813\\

\bibitem{casjobs} 
CasJobs. (n.d.). Retrieved October 09, 2016, from \url{http://skyserver.sdss.org/CasJobs/}\\


\bibitem{classic SDSS} Classic Sloan Digital Sky Survey. (n.d.). Retrieved September 18, 2016, from \url{http://classic.sdss.org/}\\

\bibitem{dr9 masks} Creating a Large Scale Structure Galaxy Catalog. (n.d.). Retrieved October 02, 2016, from \url{https://www.sdss3.org/dr9/tutorials/lss_galaxy.php}\\

\bibitem{Vaucouleurs} de Vaucouleurs, G., de Vaucouleurs, A., Corwin, H. G., Jr., et al. 1991, Third
Reference Catalogue of Bright Galaxies (New York: Springer)\\

\bibitem{Fukugita} Fukugita, M., Shimasaku, K., \& Ichikawa, T. 1995, PASP, 107, 945\\

\bibitem{Great Circle Drift Scanning} Great Circle Drift Scanning. (n.d.). Retrieved September 25, 2016, from \url{http://classic.sdss.org/dr7/products/general/edr_html/node26.html}\\

\bibitem{mangle} Mangle: Overview. (n.d.). Retrieved October 02, 2016, from \url{http://space.mit.edu/~molly/mangle/}\\

\bibitem{NED 871} NED results for object(s) in publication ``2011MNRAS.413..813C" (n.d.). Retrieved September 21, 2016, from \url{https://ned.ipac.caltech.edu/cgi-bin/nph-objsearch?search_type=Search&refcode=2011MNRAS.413..813C}\\

\bibitem{NYUVAGC} NYU Value-Added Galaxy Catalog. (n.d.). Retrieved October 02, 2016, from \url{http://sdss.physics.nyu.edu/vagc/}\\

\bibitem{SDSS-III} SDSS-III. (n.d.). Retrieved September 20, 2016, from \url{https://www.sdss3.org/}\\

\bibitem{CrossID} SDSS CrossID for DR8. (n.d.). Retrieved September 26, 2016, from \url{http://cas.sdss.org/dr8/en/tools/crossid/crossid.asp}\\

\bibitem{navigate} SDSS DR8 Navigate Tool. (n.d.). Retrieved October 01, 2016, from \url{http://skyserver.sdss.org/dr8/en/tools/chart/navi.asp}\\

\bibitem{navigate DR13} SDSS DR13 Navigate Tool. (n.d.). Retrieved October 01, 2016, from \url{http://skyserver.sdss.org/dr13/en/tools/chart/navi.aspx}\\

\bibitem{scope} SDSS Scope. (n.d.). Retrieved September 20, 2016, from \url{http://www.sdss.org/dr13/scope/}\\

\bibitem{Survey Coordinates} SDSS Survey coordinates. (n.d.). Retrieved September 25, 2016, from \url{https://www.sdss3.org/dr10/algorithms/surveycoords.php}\\

\bibitem{SQL tutorial} Searching for Data: A Tutorial. (n.d.). Retrieved September 18, 2016, from \url{http://skyserver.sdss.org/dr12/en/help/howto/search/searchhowtohome.aspx}\\

\bibitem{2MASS} Skrutskie, M. F., Cutri, R. M., Stiening, R., et al. 2006, AJ, 131, 1163\\

\bibitem{DR7 sky coverage} Sky coverage. (n.d.). Retrieved September 25, 2016, from \url{http://classic.sdss.org/dr7/coverage/}\\

\bibitem{SDSS webpage} Sloan Digital Sky Surveys. (n.d.). Retrieved September 18, 2016, from \url{http://www.sdss.org/surveys/}\\

\bibitem{instruments} Telescopes and Instruments. (n.d.). Retrieved September 20, 2016, from \url{http://www.sdss.org/instruments/}\\

\bibitem{DR8} The Eighth SDSS Data Release (DR8). (n.d.). Retrieved September 20, 2016, from \url{https://www.sdss3.org/dr8/}\\

\bibitem{DR9} The Ninth SDSS Data Release (DR9). (n.d.). Retrieved September 20, 2016, from \url{https://www.sdss3.org/dr9/}\\

\bibitem{SDSS} York, D. G., Adelman, J., Anderson, J. E., Jr., et al. 2000, AJ, 120, 1579\\

\bibitem{schema} Schema Browser. (n.d.). Retrieved September 18, 2016, from \url{http://skyserver.sdss.org/dr12/en/help/browser/browser.aspx}\\

\end{thebibliography}

\end{document}